{\Large \bf Analysing time course microarray data using Bioconductor: a case study using yeast2 Affymetrix arrays}

### 2012-07-11 paper.Rnw
Paper now includes RemoveProbes.R and ExtractIDs.R in the appendix

        } else if (before) {
            par(mar=c(3,3,2,1),  mgp=c(2,0.4,0), tck=-.01,
                cex.lab=.95,cex.axis=0.9, las=1)
        }
    }, 
    crop=hook_pdfcrop)

@

@@

<<eval=TRUE,cache=TRUE, results='hide'>>=
exp_fac = with(exp_fac, exp_fac[order(strain, tps, replicates), ])
#Construct a longitudinal object
library(GeneNet)
ngenes = 100
m = yeast.matrix[ii[1:ngenes],]
mnew = m[,exp_fac$data_order[1:15]]
mlong = as.longitudinal(t(mnew), repeats=3, time=0:4)
@

@@

As these microarrays contain probesets for both \textit{S. cerevisiae}
and \textit{S. pombe}, we first need to extract the \textit{S. cerevisiae}
data before normalisation. This can be done by filtering out the \textit{
S. pombe} data using the \verb$s_cerevisiae.msk$ file from the
Affymetrix website (see \cite{AffymetrixA}). Note that the transcript
id, i.e. the systematic orf name (obtained from \cite{AffymetrixB}) will be used for genes with no
name.

<<ExtractIDs>>=
@

@@

<<RemoveProbes>>=
@

@@

<<F3A,eval=TRUE,dev="pdf",fig.ext="pdf",cache=TRUE,out.width="0.8\\linewidth",echo=FALSE, fig.cap="Boxplots of the raw and normalised intensities. The default boxplot is to include both PM and MM intensities, whereas for the density plots in Figure~\ref{F2} the default is for only the PM intensities.">>=
par(mar=c(3,3,2,1), 
           mgp=c(2,0.4,0), tck=-.01,
               cex.axis=0.9, las=1, mfrow=c(1,2))
run_chunk("s_fig3")
@

@@

>>>>

        } else if (before) {
            par(mar=c(3,3,2,1),  mgp=c(2,0.4,0), tck=-.01,
                cex.lab=.95,cex.axis=0.9, las=1)
        }
    }, 
    crop=hook_pdfcrop)
read_chunk('ExtractIDs.R')
read_chunk('RemoveProbes.R')
@

@@

<<eval=TRUE,results='hide',message=FALSE>>=
exp_fac = with(exp_fac, exp_fac[order(strain, tps, replicates), ])
#Construct a longitudinal object
library(GeneNet)
ngenes = 100
m = yeast.matrix[ii[1:ngenes],]
mnew = m[,exp_fac$data_order[1:15]]
mlong = as.longitudinal(t(mnew), repeats=3, time=0:4)
@

@@

As these microarrays contain probesets for both \textit{S. cerevisiae}
and \textit{S. pombe}, we first need to extract the \textit{S. cerevisiae}
data before normalisation. This can be done by filtering out the \textit{
S. pombe} data using the \texttt{s\_cerevisiae.msk} file from the
Affymetrix website (see \cite{AffymetrixA}). Note that the transcript
id, i.e. the systematic orf name (obtained from \cite{AffymetrixB}) will be used for genes with no
name.

<<ExtractIDs,tidy=FALSE>>=
@

@@

<<RemoveProbes,tidy=FALSE>>=
@

@@

<<F3A,eval=TRUE,dev="pdf",fig.ext="pdf",cache=TRUE,out.width="0.8\\linewidth",echo=FALSE, message=FALSE,fig.cap="Boxplots of the raw and normalised intensities. The default boxplot is to include both PM and MM intensities, whereas for the density plots in Figure~\ref{F2} the default is for only the PM intensities.">>=
par(mar=c(3,3,2,1), 
           mgp=c(2,0.4,0), tck=-.01,
               cex.axis=0.9, las=1, mfrow=c(1,2))
run_chunk("s_fig3")
@

@@

<<echo=FALSE>>=
library(knitr)
purl("paper.Rnw")
@
